Holomorphic field theories and higher algebra

### 2022-07-10 draft.tex
small edits

\maketitle

@@

The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has had a clear role in physics.
In recent decades attention has expanded to include {\em topological} field theories (or TFTs), 
in which --- to simplify --- only the underlying smooth topology of the manifold matters.
There are, however, theories that depend on a complex structure on the manifold,
and as one might hope, these are particularly beautiful, 
just as complex variables is a particularly beautiful wing of analysis.
In essence, such {\em holomorphic} field theories have variational PDE (or ``equations of motion'') that are holomorphic:
the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
These theories admit independent motivations from mathematics and physics,
which we sketch before giving more careful definitions.

@@

\subsection{Examples from physics}
%this section aimed at physicists
%twists of SUSY theories
%Owen has some nice thoughts about globalization as it related to SUSY/THF.

@@

@@

@@

\section{Vista: Seiberg duality and its consequences}

>>>>

\maketitle
\tableofcontents

@@

The most important field theories in physics involve a metric on a manifold (whether Riemannian or Lorentzian), and hence geometry has long had a clear role in physics.
In recent decades attention has expanded to include {\em topological} field theories (or TFTs), 
in which --- to simplify --- only the underlying smooth topology of the manifold matters.
There are, however, theories that depend on a complex structure on the manifold,
and as one might hope, these are particularly beautiful, 
just as complex variables is a particularly beautiful wing of analysis.
In essence, such {\em holomorphic} field theories have variational partial differential equations (i.e., ``equations of motion'') that are holomorphic:
the PDE only involves derivatives in the holomorphic coordinates (i.e., the $\partial/\partial z_j$) and has holomorphic coefficients.
These theories admit independent motivations from mathematics and physics,
which we sketch before giving more careful definitions.

@@

\subsection{Examples}

@@

In traditional physics there are a few basic types of field theories, 
and they can be assembled into combinations in natural ways,
of which the Standard Model offers a nice example.
The basic types are\footnote{For the experts, we remark that we focus above on the core field content, and ignore (just for the moment!) issues like gauge transformations and the associated ghost fields.}
\begin{itemize}
\item {\em Scalar} field theories where the fields are maps from $M$ to a vector space $V$, or natural generalizations like taking sections of a vector bundle $V \to M$. The Higgs boson appears as part of a scalar field theory.
\item {\em Fermionic} field theories where the fields are maps from $M$ to an {\em odd} vector space or, typically, a section of a spinor bundle. Such theories are often used to describe matter, such as electron fields.
\item {\em Gauge} field theories where the fields are connections on a principal $G$-bundle over $M$, with $G$ a Lie group. The Yang--Mills theories for the electroweak and strong forces are examples.
\item $\sigma$-models where the fields are maps from $M$ into a manifold~$X$. (One can view these as generalizations of scalar field theories.)
\item {\em Gravity} theories where the fields are metrics on $M$, or something that similarly controls the geometry of $M$. Einstein's theory is a paradigmatic example.
\end{itemize}
The Standard Model involves the first three types,
and the different fields interact in intricate ways.

There are holomorphic versions of all these basic types, 
and we now spell out some simple examples.
To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
we describe them in several ways: 
in terms of PDE and action functionals but also as moduli spaces.
We do not offer a thorough justification of the dictionary, for which see \owen{cite who?}

For an example that mixes several types and that is a holomorphic analog of quantum chromodynamics (QCD), the theory that governs the strong force and quarks,
see Section~\ref{sec: seiberg}.
One motivation for us to explore holomorphic field theories is that one can translate physical insights and conjectures (such as Seiberg duality) into surprising predictions in the holomorphic setting,
which is typically much cleaner and more accessible.
(One might also hope that progress in the holomorphic setting then feeds back useful insights to physics.)

\subsubsection{Holomorphic scalar field theories}

% beta gamma systems

\subsubsection{Holomorphic fermionic field theories}

% bc systems

\subsubsection{Holomorphic gauge theories}

% BF and CS

\subsubsection{Holomorphic $\sigma$-models}

% curved beta gamma

\subsubsection{Holomorphic gravity}

% Kodaira-Spencer

@@

%this section aimed at physicists
%twists of SUSY theories
%Owen has some nice thoughts about globalization as it related to SUSY/THF.

@@

\section{Vista: Seiberg duality and its consequences}
\label{sec: seiberg}
